COG-ED Manuscript

### 2021-12-10 06_Paper/COG-ED/Manuscript.Rmd
put SV computation at the beginning and added SVs trialwise to nback df
added postcorrect indicator as regressor column to nback data frame

  # the choice column will contain 1 for the left button and 2 for the right button
  data_ED[data_ED == "EDleftbutton"] <- 1
  data_ED[data_ED == "EDrightbutton"] <- 2
  data_ED$choice <- as.numeric(data_ED$choice)

  # since only the last choice of each comparison is relevant, we will keep only those rows
  data_ED <- data_ED[data_ED$step == 6,]
  data_ED <- subset(data_ED, select = -c(step))

  # remove trials with RT < 100 ms from the n-back data and exclude trials after incorrect trials
  data_RT <- data_nback[-c(which(data_nback$rt < 0.1)), ]
  data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]

@@

>>>>

  # for the multi level model to be able to assess the influence of post-error trials, we will include that as a regressor
  # so the nback data frame will contain a column of ones and zeros

  # add the "correct" column, but shifted down by one row

  data_nback$postcorrect = c(1,data_nback$correct[1:(length(data_nback$correct)-1)])

  # make sure to avoid transfer from the previous block by marking the first trial of each block as correct

  data_nback$postcorrect[c(1,seq(64,length(data_nback$postcorrect),64))] <- 1

  # the choice column will contain 1 for the left button and 2 for the right button

  data_ED[data_ED == "EDleftbutton"] <- 1
  data_ED[data_ED == "EDrightbutton"] <- 2
  data_ED$choice <- as.numeric(data_ED$choice)

  # since only the last choice of each comparison is relevant, we will keep only those rows

  data_ED <- data_ED[data_ED$step == 6,]
  data_ED <- subset(data_ED, select = -c(step))

  # remove trials with RT < 100 ms from the n-back data and exclude trials after incorrect trials

  data_RT <- data_nback[-c(which(data_nback$rt < 0.1)), ]
  data_RT <- data_RT[-c(which(data_RT$correct == 0) + 1), ]

@@

  # add the SVs trial-wise to the nback-data-frame for the multi-level-model

  for (i in 1:nrow(data_nback)) {

    data_nback$sv[i] <- data_SV$sv[data_SV$subject == data_nback$subject[i] & data_SV$level == data_nback$level[i]]
